### 2024-10-18 Paper/MSEPM-Manuscript-Updated.tex
Update manuscript text

\subsection{Blood MSEPM Model}
We next applied the MSEPM to real data.  We utilized a large aggregated dataset composed of Illumina 450k array data from 17 publicly available datasets\cite{Ventham2016-qj,Demetriou2013-wb,Polidoro2013-xv,Johansson2013-of,Arloth2020-lo,Liu2013-dg,Soriano-Tarraga2016-uq,Chuang2017-nk,
Zannas2019-me,Kurushima2019-pe,Voisin2015-lh,Tan2014-sg,Tserel2015-ro,Butcher2017-oz,Dabin2020-iw,Marabita2013-cj,ValleG2019-xi}
 deposited in the Gene Expression Omnibus\cite{Barrett2012-gu} (GEO) generated from blood derived samples (whole blood, peripheral blood lymphocytes, and 
peripheral blood mononuclear cells). The aggregate data spanned a wide age range (0.0  - 99.0 years, Figure 3A), contained more predicted females ($n=3392$) than males ($n=2295$, Figure 3B) 
and reasonable predicted cell type abundance estimates (Figure 3C). The first principal component of a PCA modle trained cell type abundance estimates (CT-PC1) is 
largely driven by the relative abundance of granulocytes (Figure 3D), while the second PC (CT-PC2) captures relative 
differences in the abundance of differentiated lymphocytes (Figure 3D).

@@

\begin{center}
    \begin{figure}
    \includegraphics[scale=.25]{Figure1.png}    
    \footnotesize
    \caption*{\small \textbf{Figure 1:}Simulated factors and the association with simulated methylation values. (A) Age with a non-linear association with methylation 
(B). Sex (C) with a binary association with methylation (D). Normal factor (E) with a linear relationship with methylation (F). Continuous exponential
 trait (G) with a linear relationship with methylation. (I) Simulated methylation sites. Each simulation site has a starting methylation value $r^0_i$ ,
  rate of change associated with each simulated factor $r_{i, factor}$ and range of variation $\delta_i$.}
    \end{}
\end{center}

>>>>

\subsection{Blood MSEPM Model}
We next applied the MSEPM to real data.  We utilized a large aggregated dataset composed of Illumina 450k array data from 17 publicly available datasets\cite{Ventham2016-qj,Demetriou2013-wb,Polidoro2013-xv,Johansson2013-of,Arloth2020-lo,Liu2013-dg,Soriano-Tarraga2016-uq,Chuang2017-nk,
Zannas2019-me,Kurushima2019-pe,Voisin2015-lh,Tan2014-sg,Tserel2015-ro,Butcher2017-oz,Dabin2020-iw,Marabita2013-cj,ValleG2019-xi}
 deposited in the Gene Expression Omnibus\cite{Barrett2012-gu} (GEO) generated from blood derived samples (whole blood, peripheral blood lymphocytes, and 
peripheral blood mononuclear cells). The aggregate data spanned a wide age range (0.0  - 99.0 years, Figure 3A), contained more predicted females ($n=3392$) than males ($n=2295$, Figure 3B) 
and reasonable predicted cell type abundance estimates (Figure 3C). The first principal component of a PCA model trained cell type abundance estimates (CT-PC1) is 
largely driven by the relative abundance of granulocytes (Figure 3D), while the second PC (CT-PC2) captures relative 
differences in the abundance of differentiated lymphocytes (Figure 3D).

@@

\begin{center}
    \begin{figure}
    \includegraphics[scale=.25]{Figure1.png}    
    \footnotesize
    \caption*{\small \textbf{Figure 1:}Simulated factors and the association with simulated methylation values. (A) Age with a non-linear association with methylation 
(B). Sex (C) with a binary association with methylation (D). Normal factor (E) with a linear relationship with methylation (F). Continuous exponential
 trait (G) with a linear relationship with methylation. (I) Simulated methylation sites. Each simulation site has a starting methylation value $r^0_i$ ,
  rate of change associated with each simulated factor $r_{i, factor}$ and range of variation $\delta_i$.}
    \end{figure}
\end{center}
